PeakNet: An Autonomous Bragg Peak Finder with Deep Neural Networks

### 2023-06-16 manuscript.tex
Resize the runtime performance table.
Add acknowledgement

\begin{table}[t]
\caption{
    The runtime performance of diffraction image analysis algorithms measured on
    Rayonix images containing 3.7 megapixels.  We measured runtime performance
    of \psocake{} and \peaknet{} directly using Rayonix images.  For reference
    purposes, we also included another peak finding method RPF
    \citep{hadian-jaziPeakfindingAlgorithmBased2017,
    hadian-jaziDataReductionSerial2021} and two classification methods for X-ray
    diffraction data reduction. RPF runtime performance was originally measured
    on AGIPD 1M \citep{allahgholiAdaptiveGainIntegrating2019}.  
}
\label{tb : runtime}
\centering
\resizebox{\columnwidth}{!}{
\begin{tabular}{llcc}
\hline
Methods             & Hardware       & Image size         & Time (ms/event) \\ \hline
\peaknet{}          & NVIDIA 1080 Ti & 1920 $\times$ 1920 & 90.0            \\ \hline
\psocake{}          & Intel E5-2620  & 1920 $\times$ 1920 & 175.5           \\ \hline
RPF                 & Intel E5-2698  & 1024 $\times$ 1024 & 120.0           \\ \hline
%CNN hit finder      & Hit Finding  & NVIDIA 1080 Ti & 720 $\times$ 720   & 0.8             \\ \hline
%ORB+MLP             & Hit Finding  & Intel Core i5  & 720 $\times$ 720   & 50.0            \\ \hline
\end{tabular}
}
\end{table}

@@

>>>>

\begin{table*}[t]
\caption{
    The runtime performance of diffraction image analysis algorithms measured on
    Rayonix images containing 3.7 megapixels.  We measured runtime performance
    of \psocake{} and \peaknet{} directly using Rayonix images.  For reference
    purposes, we also included another peak finding method RPF
    \citep{hadian-jaziPeakfindingAlgorithmBased2017,
    hadian-jaziDataReductionSerial2021} and two classification methods for X-ray
    diffraction data reduction. RPF runtime performance was originally measured
    on AGIPD 1M \citep{allahgholiAdaptiveGainIntegrating2019}.  
}
\label{tb : runtime}
\centering
\resizebox{!}{!}{
\begin{tabular}{llcc}
\hline
Methods             & Hardware       & Image size         & Time (ms/event) \\ \hline
\peaknet{}          & NVIDIA 1080 Ti & 1920 $\times$ 1920 & 90.0            \\ \hline
\psocake{}          & Intel E5-2620  & 1920 $\times$ 1920 & 175.5           \\ \hline
RPF                 & Intel E5-2698  & 1024 $\times$ 1024 & 120.0           \\ \hline
%CNN hit finder      & Hit Finding  & NVIDIA 1080 Ti & 720 $\times$ 720   & 0.8             \\ \hline
%ORB+MLP             & Hit Finding  & Intel Core i5  & 720 $\times$ 720   & 50.0            \\ \hline
\end{tabular}
}
\end{table*}

@@

\section*{Acknowledgment}

Earlier versions utilizing the original U-Net model were built and tested by P.L under the supervision of C.H.Y.  The experiments were designed by C.W with inputs from J.B.T and C.H.Y.  C.W implemented the residual attention U-Net, prepared the datasets, labeled experimental data, and trained and evaluated the refined neural network model.  The manuscript was written by C.W and C.H.Y with input from all authors.  This material is based upon work supported by the U.S.  Department of Energy, Office of Science, Office of Basic Energy Sciences under Award Number FWP-100643.  Use of the Linac Coherent Light Source (LCLS), SLAC National Accelerator Laboratory, is supported by the U.S.  Department of Energy, Office of Science, Office of Basic Energy Sciences under Contract No.  DE-AC02-76SF00515.
